---
title: "Theatre table"
output: html_notebook
---

This notebook develops the table of utilization by day, by theatre, by session with the total number of cases, minutes(maybe with the mean and median minutes used per session).

The year is defined as the 2016 calender year.

The theatre duration is to be maximized. Start time to be the greater of Anaesthetic start or Operation start. End time is to be the latest of Operation end or Recovery takeover. Duration is defined as the difference between the start and end times.

The data set is the Raw_data set supplied by DQHI and distributed to all parties.

```{r}
#Open the libraries
library(tidyverse)
library(lubridate)
library(knitr)
```

```{r}
#declare the functions
convertTime <- function(x){
  time <- hour(x)*60 + minute(x)
  }
```

```{r}
#declare the variables
Column_names <- c(
  "Counter",
  "NHI",
  "Theatre",
  "Type",
  "Original_Ward",
  "Surgeon",
  "Surgeon_Teach",
  "Anaesthetist",
  "Anaesthetist_Teach", 
  "Anaesthetic",
  "Anaesthetist_Risk",
  "Operation_Code",
  "Operation_Code_Extention",
  "PurchaserNumber",
  "Patient_Side",
  "Specialty_OverRide",
  "Booking_In_Date",
  "Booking_In_Time",
  "Event_Date",
  "Arrival_In_Anaesthetic_Room",
  "Anaesthesia_Start",
  "Patient_Ready_for_Operation",
  "Operation_Start",
  "Operation_End",
  "Recovery_Takeover",
  "Patient_Open _Eyes_On_Command,Recovery_Complete",
  "Left_Recovery",
  "Anaesthetic_Time",
  "Operation_Time",
  "Scrub_Nurse",
  "Charge_Nurse",
  "Anaesthetic_Assist",
  "AnaestheticAssistTeach",
  "Problem_Code",
  "DirectMaterialCost",
  "Planned_Return",
  "SessionCode",
  "Verified",
  "Episode",
  "AdmissionType",
  "Modified",
  "ModifiedBy",
  "Processed",
  "Created",
  "EventComments",
  "TheatreOther",
  "PlannedOperation",
  "GRN",
  "Admission_Date",
  "AdmissionWard",
  "EpisodeNumber",
  "TimeOut",
  "UnplannedReturn",
  "Problem_Description",
  "Group_Description",
  "Specialty_Description",
  "SpecialtyCode",
  "Operation_Description"
)
```

```{r}
#read the data
Raw_data <- read_csv("/home/greig/R-projects/Clinical_audits/Theatre/OTIS_rawData.csv", col_names = Column_names, skip = 1)
#glimpse(Raw_data)
```

```{r}
#tidy the data
Raw_data$NHI <- as.factor(Raw_data$NHI)
Raw_data$Theatre <- as.factor(Raw_data$Theatre)
Raw_data$Type <- as.factor(Raw_data$Type)
Raw_data$Original_Ward <- as.factor(Raw_data$Original_Ward)
Raw_data$Surgeon <- as.factor(Raw_data$Surgeon)
Raw_data$Surgeon_Teach <- as.factor(Raw_data$Surgeon_Teach)
Raw_data$Anaesthetist <- as.factor(Raw_data$Anaesthetist)
Raw_data$Anaesthetist_Teach <- as.factor(Raw_data$Anaesthetist_Teach)
Raw_data$Anaesthetic <- as.factor(Raw_data$Anaesthetic)
Raw_data$Operation_Code <-  as.factor(Raw_data$Operation_Code)
Raw_data$Operation_Code_Extention <- as.factor(Raw_data$Operation_Code_Extention)
Raw_data$PurchaserNumber <- as.factor(Raw_data$PurchaserNumber)
Raw_data$Patient_Side <- as.factor(Raw_data$Patient_Side)
Raw_data$Specialty_OverRide <- as.factor(Raw_data$Specialty_OverRide)
Raw_data$Anaesthesia_Start <- as.character(Raw_data$Anaesthesia_Start)
Raw_data$Operation_Start <- as.character(Raw_data$Operation_Start)
Raw_data$Operation_End <- as.character(Raw_data$Operation_End)
Raw_data$Recovery_Takeover <- as.character(Raw_data$Recovery_Takeover)
Raw_data$Scrub_Nurse <-  as.factor(Raw_data$Scrub_Nurse)
Raw_data$Charge_Nurse <- as.factor(Raw_data$Charge_Nurse)
Raw_data$Anaesthetic_Assist <- as.factor(Raw_data$Anaesthetic_Assist)
Raw_data$AnaestheticAssistTeach <- as.factor(Raw_data$AnaestheticAssistTeach)
Raw_data$Problem_Code <-  as.factor(Raw_data$Problem_Code)
Raw_data$Planned_Return <- as.factor(Raw_data$Planned_Return)
Raw_data$SessionCode <- as.factor(Raw_data$SessionCode)
Raw_data$AdmissionType <- as.factor(Raw_data$AdmissionType)
Raw_data$EventComments <- as.factor(Raw_data$EventComments)
Raw_data$TheatreOther <-  as.factor(Raw_data$TheatreOther)
Raw_data$PlannedOperation <-  as.factor(Raw_data$PlannedOperation)
Raw_data$AdmissionWard <- as.factor(Raw_data$AdmissionWard)
Raw_data$EpisodeNumber <- as.factor(Raw_data$EpisodeNumber)
Raw_data$TimeOut <- as.factor(Raw_data$TimeOut)
Raw_data$UnplannedReturn <-  as.factor(Raw_data$UnplannedReturn)
Raw_data$Problem_Description <- as.factor(Raw_data$Problem_Description)
Raw_data$Group_Description <- as.factor(Raw_data$Group_Description)
Raw_data$Specialty_Description <- as.factor(Raw_data$Specialty_Description)
Raw_data$Operation_Description <- as.factor(Raw_data$Operation_Description)
#glimpse(Raw_data)
```

```{r}
#transform the data
Raw_data$Op_start <- ifelse(nchar(Raw_data$Anaesthesia_Start) == 4, Raw_data$Operation_Start, Raw_data$Anaesthesia_Start)
Raw_data$Op_start <- paste(Raw_data$Event_Date, Raw_data$Op_start, sep = " ")
Raw_data$Op_start <- dmy_hms(Raw_data$Op_start)
Raw_data$Op_start_min <- convertTime(Raw_data$Op_start)

Raw_data$Op_end <- ifelse(nchar(Raw_data$Recovery_Takeover) == 4, Raw_data$Operation_End, Raw_data$Recovery_Takeover)
Raw_data$Op_end <- paste(Raw_data$Event_Date, Raw_data$Op_end, sep = " ")
Raw_data$Op_end <- dmy_hms(Raw_data$Op_end)
Raw_data$Op_end_min <- convertTime(Raw_data$Op_end)

Raw_data$Op_duration <-  Raw_data$Op_end_min - Raw_data$Op_start_min

Raw_data$Event_Date <- dmy(Raw_data$Event_Date)

Raw_data <- Raw_data %>% 
  mutate(Month = month(Event_Date), 
         DOW = wday(Event_Date), 
         Week = week(Event_Date), 
         Day_date = yday(Event_Date))

#glimpse(Raw_data)
```

```{r}
#select the FY2016

Otis <- Raw_data %>% 
  filter(Event_Date >= "2016-07-01" & Event_Date < "2017-07-01")

#glimpse(Otis)
```

Now to select the FY 2016 and to adjust the week counter so it starts as "1" at the start of July 2016
```{r}
#Transform Otis data set

Otis$Adjusted_week <- ifelse(Otis$Week > 26, Otis$Week - 26, Otis$Week + 26)

#Declare session times as per 11.July.2017 meeting slide 11
#Stored as minutes after midnight
Morning_start <- 495 #8:15
Morning_end <- 735 #12:15
Afternoon_start <- 795 #13:15
Afternoon_end <- 1035 #17:15

glimpse(Otis)
```

```{r}
#Count Theatre 1 am

#Filter for Theatre 1 morning and count all lists
OT1_am <- Otis %>% 
  filter(Theatre == 1 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

OT1_am <- OT1_am %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

glimpse(OT1_am)

#Count Theatre 1 pm

#Filter for Theatre 1 afternoon and count all lists
OT1_pm <- Otis %>% 
  filter(Theatre == 1 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

OT1_pm <- OT1_pm %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

glimpse(OT1_pm)

TheatreTable <- full_join(OT1_am, OT1_pm, by = "Event_Date")
TheatreTable <- TheatreTable %>% 
  rename(Theatre1_am = Count.x, Theatre1_pm = Count.y)

glimpse(TheatreTable)

```

```{r}
#Count Theatre 2

#Filter for Theatre 2 morning and count all lists
OT2_am <- Otis %>% 
  filter(Theatre == 2 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

OT2_am <- OT2_am %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

TheatreTable <- full_join(TheatreTable, OT2_am, by = "Event_Date")
TheatreTable <- TheatreTable %>% 
  rename(Theatre2_am = Count)

#Filter for Theatre 2 afternoon and count all lists
OT2_pm <- Otis %>% 
  filter(Theatre == 2 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

OT2_pm <- OT2_pm %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

TheatreTable <- full_join(TheatreTable, OT2_pm, by = "Event_Date")
TheatreTable <- rename(TheatreTable, Theatre2_pm = Count)
```


```{r}
#Count Theatre 3

#Filter for Theatre 3 morning and count all lists
OT3_am <- Otis %>% 
  filter(Theatre == 3 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

OT3_am <- OT3_am %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

TheatreTable <- full_join(TheatreTable, OT3_am, by = "Event_Date")
TheatreTable <- TheatreTable %>% 
  rename(Theatre3_am = Count)

#Filter for Theatre 3 afternoon and count all lists
OT3_pm <- Otis %>% 
  filter(Theatre == 3 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

OT3_pm <- OT3_pm %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

TheatreTable <- full_join(TheatreTable, OT3_pm, by = "Event_Date")
TheatreTable <- rename(TheatreTable, Theatre3_pm = Count)
```

```{r}
#Count Theatre 4

#Filter for Theatre 4 morning and count all lists
OT4_am <- Otis %>% 
  filter(Theatre == 4 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

OT4_am <- OT4_am %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

TheatreTable <- full_join(TheatreTable, OT4_am, by = "Event_Date")
TheatreTable <- TheatreTable %>% 
  rename(Theatre4_am = Count)

#Filter for Theatre 4 afternoon and count all lists
OT4_pm <- Otis %>% 
  filter(Theatre == 4 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

OT4_pm <- OT4_pm %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

TheatreTable <- full_join(TheatreTable, OT4_pm, by = "Event_Date")
TheatreTable <- rename(TheatreTable, Theatre4_pm = Count)
```

```{r}
#Count Theatre 5

#Filter for Theatre 5 morning and count all lists
OT5_am <- Otis %>% 
  filter(Theatre == 5 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

OT5_am <- OT5_am %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

TheatreTable <- full_join(TheatreTable, OT5_am, by = "Event_Date")
TheatreTable <- TheatreTable %>% 
  rename(Theatre5_am = Count)

#Filter for Theatre 5 afternoon and count all lists
OT5_pm <- Otis %>% 
  filter(Theatre == 5 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

OT5_pm <- OT5_pm %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

TheatreTable <- full_join(TheatreTable, OT5_pm, by = "Event_Date")
TheatreTable <- rename(TheatreTable, Theatre5_pm = Count)
```

```{r}
#Count Theatre 6

#Filter for Theatre 6 morning and count all lists
OT6_am <- Otis %>% 
  filter(Theatre == 6 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

OT6_am <- OT6_am %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

TheatreTable <- full_join(TheatreTable, OT6_am, by = "Event_Date")
TheatreTable <- TheatreTable %>% 
  rename(Theatre6_am = Count)

#Filter for Theatre 6 afternoon and count all lists
OT6_pm <- Otis %>% 
  filter(Theatre == 6 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

OT6_pm <- OT6_pm %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

TheatreTable <- full_join(TheatreTable, OT6_pm, by = "Event_Date")
TheatreTable <- rename(TheatreTable, Theatre6_pm = Count)
```

```{r}
#Count Theatre 7

#Filter for Theatre 7 morning and count all lists
OT7_am <- Otis %>% 
  filter(Theatre == 7 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

OT7_am <- OT7_am %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

TheatreTable <- full_join(TheatreTable, OT7_am, by = "Event_Date")
TheatreTable <- TheatreTable %>% 
  rename(Theatre7_am = Count)

#Filter for Theatre 7 afternoon and count all lists
OT7_pm <- Otis %>% 
  filter(Theatre == 7 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

OT7_pm <- OT7_pm %>% 
  group_by(Event_Date) %>% 
  summarise(Count = n())

TheatreTable <- full_join(TheatreTable, OT7_pm, by = "Event_Date")
TheatreTable <- rename(TheatreTable, Theatre7_pm = Count)

glimpse(TheatreTable)
```

```{r}
#transpose and export TheatreTable

YearMatch <- read_csv("/home/greig/R-projects/Clinical_audits/Theatre/yearMatch.csv", col_names = "Event_Date")
YearMatch$Event_Date <- dmy(YearMatch$Event_Date)

TheatreTable_export <- full_join(YearMatch, TheatreTable, by = "Event_Date")

TheatreTable <- arrange(TheatreTable, Event_Date)

write.table(TheatreTable_export, file = "/home/greig/R-projects/Clinical_audits/Theatre/TheatreTable.csv", row.names = FALSE, sep = ",")

```

```{r}
#export event ID to gather CWD data.

Event_ID <- Otis %>% 
  select(TimeOut)

write.table(Event_ID, "/home/greig/R-projects/Clinical_audits/Theatre/CWD.csv", sep = ",", row.names = FALSE)
```

```{r}
#Countand allocate the minutes used in Theatre 1 am

#Filter for Theatre 1 morning and count all lists
Min_1am <- Otis %>% 
  filter(Theatre == 1 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

Min_1am <- Min_1am %>% 
  group_by(Event_Date) %>% 
  summarise(
    Session_start_1am = min(Op_start_min),
    Session_end_1am = max(Op_end_min),
    Session_min_used_1am = sum(Op_duration)) %>% 
  ungroup()

Min_1am <- Min_1am %>% 
  mutate(
    Late_start_min_1am = Morning_start - Session_start_1am,
    Early_finish_min_1am = Session_end_1am - Morning_end,
    Session_gap_1am = 240 - Session_min_used_1am + Late_start_min_1am + Early_finish_min_1am)


#Count and allocate the minutes used in  Theatre 1 pm

#Filter for Theatre 1 afternoon and count all lists
Min_1pm <- Otis %>% 
  filter(Theatre == 1 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

Min_1pm <- Min_1pm %>% 
  group_by(Event_Date) %>% 
  summarise(
    Session_start_1pm = min(Op_start_min),
    Session_end_1pm = max(Op_end_min),
    Session_min_used_1pm = sum(Op_duration)) %>% 
  ungroup()

Min_1pm <- Min_1pm %>% 
  mutate(
    Late_start_min_1pm = Afternoon_start - Session_start_1pm,
    Early_finish_min_1pm = Session_end_1pm - Afternoon_end,
    Session_gap_1pm = 240 - Session_min_used_1pm + Late_start_min_1pm + Early_finish_min_1pm)

Min_1am$Overrun_min_1am <- ifelse(Min_1am$Early_finish_min_1am > 0, Min_1am$Early_finish_min_1am, 0)
Min_1am$Early_finish_min_1am <- ifelse(Min_1am$Early_finish_min_1am > 0, 0, Min_1am$Early_finish_min_1am)
Min_1pm$Overrun_min_1pm <- ifelse(Min_1pm$Early_finish_min_1pm > 0, Min_1pm$Early_finish_min_1pm, 0)
Min_1pm$Early_finish_min_1pm <- ifelse(Min_1pm$Early_finish_min_1pm > 0, 0, Min_1pm$Early_finish_min_1pm)

MinuteTable <- full_join(Min_1am, Min_1pm, by = "Event_Date")

glimpse(MinuteTable)
```

```{r}
#Count and allocate the minutes used in Theatre 2 am

#Filter for Theatre 2 morning and count all lists
Min_2am <- Otis %>% 
  filter(Theatre == 2 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

Min_2am <- Min_2am %>% 
  group_by(Event_Date) %>% 
  summarise(
    Session_start_2am = min(Op_start_min),
    Session_end_2am = max(Op_end_min),
    Session_min_used_2am = sum(Op_duration)) %>% 
  ungroup()

Min_2am <- Min_2am %>% 
  mutate(
    Late_start_min_2am = Morning_start - Session_start_2am,
    Early_finish_min_2am = Session_end_2am - Morning_end,
    Session_gap_2am = 240 - Session_min_used_2am + Late_start_min_2am + Early_finish_min_2am)

Min_2am$Overrun_min_2am <- ifelse(Min_2am$Early_finish_min_2am > 0, Min_2am$Early_finish_min_2am, 0)
Min_2am$Early_finish_min_2am <- ifelse(Min_2am$Early_finish_min_2am > 0, 0, Min_2am$Early_finish_min_2am)

MinuteTable <-  full_join(MinuteTable, Min_2am, by = "Event_Date")

#Count and allocate the minutes used in Theatre 2 pm

#Filter for Theatre 2 afternoon and count all lists
Min_2pm <- Otis %>% 
  filter(Theatre == 2 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

Min_2pm <- Min_2pm %>% 
  group_by(Event_Date) %>% 
  summarise(
    Session_start_2pm = min(Op_start_min),
    Session_end_2pm = max(Op_end_min),
    Session_min_used_2pm = sum(Op_duration)) %>% 
  ungroup()

Min_2pm <- Min_2pm %>% 
  mutate(
    Late_start_min_2pm = Afternoon_start - Session_start_2pm,
    Early_finish_min_2pm = Session_end_2pm - Afternoon_end,
    Session_gap_2pm = 240 - Session_min_used_2pm + Late_start_min_2pm + Early_finish_min_2pm)

Min_2pm$Overrun_min_2pm <- ifelse(Min_2pm$Early_finish_min_2pm > 0, Min_2pm$Early_finish_min_2pm, 0)
Min_2pm$Early_finish_min_2pm <- ifelse(Min_2pm$Early_finish_min_2pm > 0, 0, Min_2pm$Early_finish_min_2pm)

MinuteTable <- full_join(MinuteTable, Min_2pm, by = "Event_Date")

```


```{r}
#Count and allocate the minutes used in Theatre 3 am

#Filter for Theatre 3 morning and count all lists
Min_3am <- Otis %>% 
  filter(Theatre == 3 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

Min_3am <- Min_3am %>% 
  group_by(Event_Date) %>% 
  summarise(
    Session_start_3am = min(Op_start_min),
    Session_end_3am = max(Op_end_min),
    Session_min_used_3am = sum(Op_duration)) %>% 
  ungroup()

Min_3am <- Min_3am %>% 
  mutate(
    Late_start_min_3am = Morning_start - Session_start_3am,
    Early_finish_min_3am = Session_end_3am - Morning_end,
    Session_gap_3am = 240 - Session_min_used_3am + Late_start_min_3am + Early_finish_min_3am)

Min_3am$Overrun_min_3am <- ifelse(Min_3am$Early_finish_min_3am > 0, Min_3am$Early_finish_min_3am, 0)
Min_3am$Early_finish_min_3am <- ifelse(Min_3am$Early_finish_min_3am > 0, 0, Min_3am$Early_finish_min_3am)

MinuteTable <-  full_join(MinuteTable, Min_3am, by = "Event_Date")

#Count and allocate the minutes used in Theatre 3 pm

#Filter for Theatre 3 afternoon and count all lists
Min_3pm <- Otis %>% 
  filter(Theatre == 3 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

Min_3pm <- Min_3pm %>% 
  group_by(Event_Date) %>% 
  summarise(
    Session_start_3pm = min(Op_start_min),
    Session_end_3pm = max(Op_end_min),
    Session_min_used_3pm = sum(Op_duration)) %>% 
  ungroup()

Min_3pm <- Min_3pm %>% 
  mutate(
    Late_start_min_3pm = Afternoon_start - Session_start_3pm,
    Early_finish_min_3pm = Session_end_3pm - Afternoon_end,
    Session_gap_3pm = 240 - Session_min_used_3pm + Late_start_min_3pm + Early_finish_min_3pm)

Min_3pm$Overrun_min_3pm <- ifelse(Min_3pm$Early_finish_min_3pm > 0, Min_3pm$Early_finish_min_3pm, 0)
Min_3pm$Early_finish_min_3pm <- ifelse(Min_3pm$Early_finish_min_3pm > 0, 0, Min_3pm$Early_finish_min_3pm)

MinuteTable <- full_join(MinuteTable, Min_3pm, by = "Event_Date")
```

```{r}
#Count and allocate the minutes used in Theatre 5 am

#Filter for Theatre 5 morning and count all lists
Min_5am <- Otis %>% 
  filter(Theatre == 5 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

Min_5am <- Min_5am %>% 
  group_by(Event_Date) %>% 
  summarise(
    Session_start_5am = min(Op_start_min),
    Session_end_5am = max(Op_end_min),
    Session_min_used_5am = sum(Op_duration)) %>% 
  ungroup()

Min_5am <- Min_5am %>% 
  mutate(
    Late_start_min_5am = Morning_start - Session_start_5am,
    Early_finish_min_5am = Session_end_5am - Morning_end,
    Session_gap_5am = 240 - Session_min_used_5am + Late_start_min_5am + Early_finish_min_5am)

Min_5am$Overrun_min_5am <- ifelse(Min_5am$Early_finish_min_5am > 0, Min_5am$Early_finish_min_5am, 0)
Min_5am$Early_finish_min_5am <- ifelse(Min_5am$Early_finish_min_5am > 0, 0, Min_5am$Early_finish_min_5am)

MinuteTable <-  full_join(MinuteTable, Min_5am, by = "Event_Date")

#Count and allocate the minutes used in Theatre 5 pm

#Filter for Theatre 5 afternoon and count all lists
Min_5pm <- Otis %>% 
  filter(Theatre == 5 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

Min_5pm <- Min_5pm %>% 
  group_by(Event_Date) %>% 
  summarise(
    Session_start_5pm = min(Op_start_min),
    Session_end_5pm = max(Op_end_min),
    Session_min_used_5pm = sum(Op_duration)) %>% 
  ungroup()

Min_5pm <- Min_5pm %>% 
  mutate(
    Late_start_min_5pm = Afternoon_start - Session_start_5pm,
    Early_finish_min_5pm = Session_end_5pm - Afternoon_end,
    Session_gap_5pm = 240 - Session_min_used_5pm + Late_start_min_5pm + Early_finish_min_5pm)

Min_5pm$Overrun_min_5pm <- ifelse(Min_5pm$Early_finish_min_5pm > 0, Min_5pm$Early_finish_min_5pm, 0)
Min_5pm$Early_finish_min_5pm <- ifelse(Min_5pm$Early_finish_min_5pm > 0, 0, Min_5pm$Early_finish_min_5pm)

MinuteTable <- full_join(MinuteTable, Min_5pm, by = "Event_Date")
```

```{r}
#Count and allocate the minutes used in Theatre 6 am

#Filter for Theatre 6 morning and count all lists
Min_6am <- Otis %>% 
  filter(Theatre == 6 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

Min_6am <- Min_6am %>% 
  group_by(Event_Date) %>% 
  summarise(
    Session_start_6am = min(Op_start_min),
    Session_end_6am = max(Op_end_min),
    Session_min_used_6am = sum(Op_duration)) %>% 
  ungroup()

Min_6am <- Min_6am %>% 
  mutate(
    Late_start_min_6am = Morning_start - Session_start_6am,
    Early_finish_min_6am = Session_end_6am - Morning_end,
    Session_gap_6am = 240 - Session_min_used_6am + Late_start_min_6am + Early_finish_min_6am)

Min_6am$Overrun_min_6am <- ifelse(Min_6am$Early_finish_min_6am > 0, Min_6am$Early_finish_min_6am, 0)
Min_6am$Early_finish_min_6am <- ifelse(Min_6am$Early_finish_min_6am > 0, 0, Min_6am$Early_finish_min_6am)

MinuteTable <-  full_join(MinuteTable, Min_6am, by = "Event_Date")

#Count and allocate the minutes used in Theatre 6 pm

#Filter for Theatre 6 afternoon and count all lists
Min_6pm <- Otis %>% 
  filter(Theatre == 6 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

Min_6pm <- Min_6pm %>% 
  group_by(Event_Date) %>% 
  summarise(
    Session_start_6pm = min(Op_start_min),
    Session_end_6pm = max(Op_end_min),
    Session_min_used_6pm = sum(Op_duration)) %>% 
  ungroup()

Min_6pm <- Min_6pm %>% 
  mutate(
    Late_start_min_6pm = Afternoon_start - Session_start_6pm,
    Early_finish_min_6pm = Session_end_6pm - Afternoon_end,
    Session_gap_6pm = 240 - Session_min_used_6pm + Late_start_min_6pm + Early_finish_min_6pm)

Min_6pm$Overrun_min_6pm <- ifelse(Min_6pm$Early_finish_min_6pm > 0, Min_6pm$Early_finish_min_6pm, 0)
Min_6pm$Early_finish_min_6pm <- ifelse(Min_6pm$Early_finish_min_6pm > 0, 0, Min_6pm$Early_finish_min_6pm)

MinuteTable <- full_join(MinuteTable, Min_6pm, by = "Event_Date")
```

```{r}
#Count and allocate the minutes used in Theatre 7 am

#Filter for Theatre 7 morning and count all lists
Min_7am <- Otis %>% 
  filter(Theatre == 7 & Morning_start <= Op_start_min & Op_start_min <= Morning_end)

Min_7am <- Min_7am %>% 
  group_by(Event_Date) %>% 
  summarise(
    Session_start_7am = min(Op_start_min),
    Session_end_7am = max(Op_end_min),
    Session_min_used_7am = sum(Op_duration)) %>% 
  ungroup()

Min_7am <- Min_7am %>% 
  mutate(
    Late_start_min_7am = Morning_start - Session_start_7am,
    Early_finish_min_7am = Session_end_7am - Morning_end,
    Session_gap_7am = 240 - Session_min_used_7am + Late_start_min_7am + Early_finish_min_7am)

Min_7am$Overrun_min_7am <- ifelse(Min_7am$Early_finish_min_7am > 0, Min_7am$Early_finish_min_7am, 0)
Min_7am$Early_finish_min_7am <- ifelse(Min_7am$Early_finish_min_7am > 0, 0, Min_7am$Early_finish_min_7am)

MinuteTable <-  full_join(MinuteTable, Min_7am, by = "Event_Date")

#Count and allocate the minutes used in Theatre 7 pm

#Filter for Theatre 7 afternoon and count all lists
Min_7pm <- Otis %>% 
  filter(Theatre == 7 & Afternoon_start <= Op_start_min & Op_start_min <= Afternoon_end)

Min_7pm <- Min_7pm %>% 
  group_by(Event_Date) %>% 
  summarise(
    Session_start_7pm = min(Op_start_min),
    Session_end_7pm = max(Op_end_min),
    Session_min_used_7pm = sum(Op_duration)) %>% 
  ungroup()

Min_7pm <- Min_7pm %>% 
  mutate(
    Late_start_min_7pm = Afternoon_start - Session_start_7pm,
    Early_finish_min_7pm = Session_end_7pm - Afternoon_end,
    Session_gap_7pm = 240 - Session_min_used_7pm + Late_start_min_7pm + Early_finish_min_7pm)

Min_7pm$Overrun_min_7pm <- ifelse(Min_7pm$Early_finish_min_7pm > 0, Min_7pm$Early_finish_min_7pm, 0)
Min_7pm$Early_finish_min_7pm <- ifelse(Min_7pm$Early_finish_min_7pm > 0, 0, Min_7pm$Early_finish_min_7pm)

MinuteTable <- full_join(MinuteTable, Min_7pm, by = "Event_Date")
```

```{r}
YearMatch <- read_csv("/home/greig/R-projects/Clinical_audits/Theatre/yearMatch.csv", col_names = "Event_Date")
YearMatch$Event_Date <- dmy(YearMatch$Event_Date)

MinuteTable_export <- full_join(YearMatch, MinuteTable, by = "Event_Date")

MinuteTable <- arrange(MinuteTable, Event_Date)

write.table(MinuteTable, file = "/home/greig/R-projects/Clinical_audits/Theatre/MinuteTable.csv", row.names = FALSE, sep = ",")
```

